\chapter{Introduction}
{\it A programmer has this intelligent idea to develop a system that will change the world, this system is so big that it might need more than one developer to make it happen, even if the programmer decides to do it alone, he needs to develop it in such a way that he can handle its complexity.}

From the story above, the question "how can one effectively develop a complex software system that is flexible, extensible, manageable and maintainable?" is derived, this is the question I hope to answer in this thesis. 

{\bf Software development} have become a crucial part of our community today, as almost every business, research, 
experimental and educational sector requires software solutions to problems. With this comes a high need to develop
good software systems that not only serve the required functionalities, but also is flexible, extensible and efficient. This 
softwares are developed by {\bf Software Developers}, whom face problems of their own, problems such as good development
processes and methodologies that enables them develop systems efficiently, deliver software products on time, ease in
both development and management, and cope with the ever changing of software requirements.


Through the period of my studies, I have come to discover, attain and apply various set of skills ranging from creativity, research, critical thinking, problem solving, to the whole process involved in software engineering such as; requirements gathering, software design, implementation, testing and management of evolving systems. Though I had lots of challenges during the course of my studies, I have come to develop interest in Application of Artificial Intelligence such as Computer Vision, Intelligent Agents and Robotics, Software development on Desktop, Mobile and Embedded platforms, Modular Systems, programming methods, paradigms and methodologies. 


Mobile market is one of the biggest markets of our time, with more and more mobile platforms being developed. Android have been at the top of the market with over 52 percent of the market and with over 1.5 million android devices activated per day. It is very clear that this is where every developer will want to be. Besides the joy of writing applications that will possibly be used by millions of people, developing solutions to problems faced by developers of this platform happens to be of great interest to me.


I have done some development on Android platform, explored its various features and this lead me to conceptualize various ways i can simplify and develop complex systems. Being a man of structure and simplicity in terms of software development, discovering modular development was a great breakthrough for me, though this method have existed for quite a while now some might view it as old fashion and ineffective. Breaking a complex system into smaller chunks (modules) based on functionalities and developing each module independently with little or no connection to others seems so intelligible and exquisite to me.


In the chapters to come, I am going to discourse and explore the concept of modularity in software development, why it is important and how it can be achieved. With the aid of the android software system i developed using both the native development tool Android SDK with Java and Kivy Framework with Python, I will explain and show how this method can be applied. Development using both of this environment was an idea from my supervisor Dr. Attila Adamko, which turns out to be a really good one in terms of making the points of this thesis.
